Postural developments modulate children's visual access to social information

### 2018-05-11 writeup-cogsci/cogsci2018_cameraReady.Rmd
still a few lines over but much closer

```
# Introduction
From early infancy, children are deeply engaged in learning from others [@csibra2009natural; @meltzoff2007like]. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development]. Further, when infants attend to video stimuli, they tend to look mostly at faces at the expense of other visual information -- though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

@@

```{r detByPosOrient, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=6, fig.height=3, fig.cap = "Proportion of face and wrist detections in each age group as a function of children's posture (top panel) and orientation (bottom panel)."}

@@

# General Discussion
We used a head-mounted camera to explore how children's postural and locomotor development affects their visual access to social information, here operationalized as the presence of the faces and hands of their caregiver. Children's posture and orientation towards their caregiver changed systematically across age, and both of these factors influenced the proportion of faces and hands that were available in the child's visual field. Though we oriented our cameras to maximally capture face information, we nonetheless saw an influence of orientation and posture on visual access to hands. This work suggests that motor development modulates how infants experience their visual world and the social information in it: Infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.

>>>>

```
# Introduction
From early infancy, children are deeply engaged in learning from others. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development]. Further, when infants attend to video stimuli, they tend to look mostly at faces at the expense of other visual information -- though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

@@

```{r detByPosOrient, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=6, fig.height=3, fig.cap = "Proportion of face / wrist detections by children's age, posture (top panel), and orientation (bottom panel)."}

@@

# General Discussion
We used a head-mounted camera to explore how children's postural and locomotor development affects their visual access to social information, here operationalized as the presence of the faces and hands of their caregiver. Children's posture and orientation towards their caregiver changed systematically across age, and both of these factors influenced the proportion of faces and hands in the child's visual field. Though our cameras were oriented to capture face information, we nonetheless saw an influence of orientation and posture on visual access to hands. Motor development appears to modulate how infants experience their visual world and the social information in it.

### 2018-05-11 writeup-cogsci/cogsci2018_cameraReady.tex
still a few lines over but much closer

From early infancy, children are deeply engaged in learning from others
(Csibra \& Gergely, 2009; Meltzoff, 2007). Even newborns tend to prefer
to look at faces with direct vs.~averted gaze (Farroni, Csibra, Simion,
\& Johnson, 2002) and young infants follow overt gaze shifts
(Gredeb\wrapmf{\"{a}}ck, Fikke, \& Melinder, 2010). Further, when
infants attend to video stimuli, they tend to look mostly at faces at
the expense of other visual information -- though older infants start to
look towards people's hands and the actions they are performing (Frank,
Amso, \& Johnson, 2014; Frank, Vul, \& Saxe, 2012).

@@

\caption[Proportion of face and wrist detections in each age group as a function of children's posture (top panel) and orientation (bottom panel)]{Proportion of face and wrist detections in each age group as a function of children's posture (top panel) and orientation (bottom panel).}\label{fig:detByPosOrient}
\end{figure*}
\end{CodeChunk}

@@

We used a head-mounted camera to explore how children's postural and
locomotor development affects their visual access to social information,
here operationalized as the presence of the faces and hands of their
caregiver. Children's posture and orientation towards their caregiver
changed systematically across age, and both of these factors influenced
the proportion of faces and hands that were available in the child's
visual field. Though we oriented our cameras to maximally capture face
information, we nonetheless saw an influence of orientation and posture
on visual access to hands. This work suggests that motor development
modulates how infants experience their visual world and the social
information in it: Infants that are sitting and standing have a
different view of their world, the people in it, and the actions that
are being performed.

@@

\hypertarget{ref-csibra2009natural}{}
Csibra, G., \& Gergely, G. (2009). Natural pedagogy. \emph{Trends in
Cognitive Sciences}, \emph{13}(4), 148--153.

@@

\hypertarget{ref-meltzoff2007like}{}
Meltzoff, A. N. (2007). ``Like me'': A foundation for social cognition.
\emph{Developmental Science}, \emph{10}(1), 126--134.

>>>>

From early infancy, children are deeply engaged in learning from others.
Even newborns tend to prefer to look at faces with direct vs.~averted
gaze (Farroni, Csibra, Simion, \& Johnson, 2002) and young infants
follow overt gaze shifts (Gredeb\wrapmf{\"{a}}ck, Fikke, \& Melinder,
2010). Further, when infants attend to video stimuli, they tend to look
mostly at faces at the expense of other visual information -- though
older infants start to look towards people's hands and the actions they
are performing (Frank, Amso, \& Johnson, 2014; Frank, Vul, \& Saxe,
2012).

@@

\caption[Proportion of face / wrist detections by children's age, posture (top panel), and orientation (bottom panel)]{Proportion of face / wrist detections by children's age, posture (top panel), and orientation (bottom panel).}\label{fig:detByPosOrient}
\end{figure*}
\end{CodeChunk}

@@

We used a head-mounted camera to explore how children's postural and
locomotor development affects their visual access to social information,
here operationalized as the presence of the faces and hands of their
caregiver. Children's posture and orientation towards their caregiver
changed systematically across age, and both of these factors influenced
the proportion of faces and hands in the child's visual field. Though
our cameras were oriented to capture face information, we nonetheless
saw an influence of orientation and posture on visual access to hands.
Motor development appears to modulate how infants experience their
visual world and the social information in it.

@@

@@
